A survey of HTTP caching implementations on the open Semantic Web

### 2015-02-21 sanity/paper1.tex
Move citation
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1040 43ef1190-90fd-4dd7-a769-d0121f02b80e

The \cite{dyldo2} Dynamic Linked Data Observatory (DyLDO) performed,
and continues to do so, monitoring of parts of the Linked Open Data
Cloud to determine dynamicity characteristics of Linked Data. Caching
is one of their motivations, but they have not published statistics on
HTTP headers.

>>>>

The Dynamic Linked Data Observatory (DyLDO) \cite{dyldo2} performed,
and continues to do so, monitoring of parts of the Linked Open Data
Cloud to determine dynamicity characteristics of Linked Data. Caching
is one of their motivations, but they have not published statistics on
HTTP headers.
